European or American? A re-examination of the transatlantic influence over the IMF

### 2025-08-13 manuscript/manuscript.qmd
Remove "potentially"

While our baseline results indicate that European powers exert substantial influence over IMF lending outcomes, two plausible explanations could potentially account for these patterns without implying broad, institutionalised influence.

>>>>

While our baseline results indicate that European powers exert substantial influence over IMF lending outcomes, two plausible explanations could account for these patterns without implying broad, institutionalised influence.
